# (Base) Model Construction 基础模型搭建

## Intro on (Base) Model Design and Construction 模型设计搭建概要
```{r message=FALSE, warning=FALSE, include=FALSE}
### Load packages
library(tsibble)
library(lubridate)
library(tidyverse)
library(quantmod)
library(rvest) 
library(xts)
library(TTR)
library(rvest)
library(zoo)
library(knitr)
library(kableExtra)
library(plotly)
# nasdaq api 44D9F6_XzqEy8xstEuxb
```

The model designing to select stocks is heavily dependent on the portfolio strategy and risk preferences.
To reiterate, the `base model` will select stocks signaling near-term investment opportunities based on a combination of **technical indicators**.

Over 6,000 stocks currently listed in the U.S. security market, however, some may not be appropriate for the portfolio (style, risk, compliance, etc.).
For instance, a stock went public one year ago with a market cap of \$10B does not satisfy the investment style and risk reference.
To save computing power, the model will subjectively filter out these 'inappropriate' stocks in advance to any machine selection processes based on indication signals.

翻译

More specifically:

* Step 1: Fetch market data:

The model will gather up-to-date raw trading data and statistics (open, close, volume etc.) for stocks currently listed on the NYSE and NASDAQ (U.S. stocks listed on the following exchanges: PHLX, MS4X, BSE, CHX, and NSX are excluded in this study).

翻译

* Step 2: Drop ‘nonviable’ stocks (Portfolio-specific Filters):

First, the **subjective filters** eliminate the ‘inappropriate’ stocks, which are the ones will not be considered as a viable investment option; because of the unmatched management styles, internal risk management guidelines, risk preference, investor/client investment preferences/risk tolerance, etc. (subjective: the eliminated securities are due to subjective preset investment goals, management styles or risk management guidelines; but may be stocks could bring substantial future returns).

翻译

* Step 3: Calculate the indicators (Technical Indicators Construction):

There are countless of technical indicators, and we will first pick a pool of indicators we deem fit in characterizing the U.S equity price performances.
Following, with a programmatic approach, the model computes the indicator value(s), and produces any meaningful graphs.
In terms of trading signals, we will set conventional signal parameters, where further investment-specific setting adjustments may become necessary.
Moreover, we will use a handful of widely-traded stocks to test whether the program for each technical indicators perform by providing trading signals as intended (not a test on signal accuracy).

翻译

* Step 4: Select a combination of significant technical indicators (Technical Indicator Effectiveness Ranking)

The characteristics and preset assumptions of the technical indicators, meaning they behave differently for each market with every security.
For instance, one can be an effective indicator in terms of signaling accuracy for a stock in a more traded sector, may not hold the case for another stock which is less liquid.
Similar applies to the indicator parameters, where different parameter settings may lead to opposite trading signals during different periods.
Whether the following indicators are effective and accurate is questionable.
Thus, the model utilizes a ranking system to objectively determine their effectiveness, i.e. **significant** indicators. Using technical indicators in reaching a profitable trading decision requires jurisprudence coupled with investment experience.

The model methodology is to use the full dataset with all 5,400+ stocks currently listed on NYSE and NASDAQ, to test and rank the technical indicators in terms of the accuracy in giving the correct trading signals (1,997 NYSE, 3,433 NASDAQ as of Feb 22, 2024).
For example, say the RSI accuracy is 70% and No.1 among all technical indicators, by giving the correct next-day trading signals for 3,780+ stocks week-long; which its signal accuracy is higher than any other indicators.
With a programmatic approach, the effectiveness evaluation processes produce an accuracy-based ranking for all input technical indicators.

翻译

However, using a technical-only based model emerges a practical and tricky issue, where one **significant** indicator may disagree with another **significant** indicator on trading signals.
A subjective set of indicator parameters may also cause similar mixed-signal issues.
In practice, analysts and PMs reference a combination of the technical indicators, along with other security analysis methods (fundamental, quant, etc.) before arriving at a trading decision (Buy/Sell/Hold).

Moreover, investment strategies usually vary for different fund products.
To have the stock selection model becoming more adaptive and customizable for various investment needs; for example, to be able to output two separate top-30 stock lists for a buy-and-hold strategy and a long-short risk-neutral strategy.
Therefore, the model not only need to be adaptive to input different sets of significant technical indicators (example: 2 sets of technical indicators to **signal for shorter-and-longer-term returns**), but also for numerous combinations of parameter settings.

翻译

More specifically (for Step 4), the model first utilizes the full (U.S. stock) dataset to test and rank the effectiveness of all input technical indicators, and produces two combinations of significant technical indicators, one set for shorter-term (intraday, next day) signals and one set for longer-term signals.

Regarding the parameter settings for the technical indicators, the process in determining the ‘best’ setting is relatively subjective.
It requires manual adjustments for each (of them who needs a parameter input), in which different settings at different sample (testing) periods may result differently.
Most importantly, trading signals directly influenced by the parameter settings; and the investment styles/goals also have direct impact on the settings (e.g. an aggressive strategy, a trend-following strategy, and an EIF strategy certainly requires different parameter settings, and similar applies to initiate trades on the left or right).

翻译

* Step 5: Stock Selection & Trading Signals – the Base Model By finishing the process of datasets inputs, and the elimination of stocks on portfolio-specific (‘nonviable’) filters, the (base) stock selection model can now fetch the up-to-date stock trading statistics through the chosen combinations of significant technical indicators.

By design, every technical indicator generates a trading signal based on the given parameter settings for each stock.
Following, the model counts the number of trading signals generated for each stock.

An aggregate signaling rule needs to be established in advance for the model to generate the trading recommendation, however, this setting can be modified easily to suit specific investment needs and the continuously changing market landscape.

翻译

For example, the PMs can set the rule with a **(theoretical) winning-probability threshold** of 75%, and say from the model output, `stock A` generated 11 `short position` signals from a total of 14 significant technical indicators, which $\frac{11}{14}>75\%$.
The stock-selection model which indicated that `stock A` has a(n) aggregate *SELL* signal as of today.
Obviously, with the subjective setting of the winning probability threshold, the programming approach of the model can automate the tedious and heavy computing process, and produces a list of `BUY` stocks, and a list of `SELL` stocks.

Furthermore, to suit various investment goals/needs like multiple strategies for different portfolios; the model input can easily be modified into two combinations of technical indicators.
As an example, besides generating trading recommendations (BUY/SELL/HOLD) for each stock, the model can further indicate/signal whether which stocks have the investment potential (either direction) for a longer-term (Note: such additional recommendation may be due to the extra combination of technical indicators and/or different indicator settings).

Above summarized the complete processes in detail, to construct an adaptative U.S. stock selection model using only technical indicators (i.e. `the base model`) and to generate trading recommendations accordingly.

翻译

Note: We believe technical indicators are relatively objective as they are derivations of market data and statistics.
Therefore, by theory, such model should include the less randomness and bias in trading recommendations.
To control portfolio drawdowns, while seeking for higher risk-adjusted returns, we purposely divide the model into two parts and introduce model factors/indicators stepwise.
Other types of analytical data and statistics include somewhat subjectivity, however, the complete stock selection model (i.e. `the full model`) (*Section 5*) will accept significant fundamental, growth/value, volatility, and emotion factors.

翻译

* Step 6: Base Model Back-test and RM Additions (Portfolio Simulation [Setting: Base Model, Allocation: Equal Weight])

After gathered the recommended list of stocks to invest generated by the `base model`, the program is set to evaluate the model performance.
A standard back-test is then performed, in which the portfolio is constituted by the model-selected U.S. stocks.
Trades are set to execute in accordance with the model-generated trading signals (BUY/SELL/HOLD), and the set theoretical winning-probability threshold (the aggregate signaling rule).
For the simplicity and the purpose in controlling variables, the asset allocation rule for this simulated portfolio is set to be equal weight.
Finally, the program computes the investment return of the simulated portfolio in percentages.

In constructing a model to select U.S. equities, and assess the strategy performance, we assumed a stock-only portfolio.
In practice, we need to consider the risk exposure.
Effective and proactice risk management is essential for a stock-heavy portfolio.
For instance, depends on the overall volatility from the selected stocks, the PMs can invest in ETFs or appropriate commodities or keep a higher cash or cash equivalent asset to hedge.

翻译

<insert.png> [model design flow chart]

Above has explained in great details about the expectations of the price volume strategy, the philosophy in designing the stock selection model and the necessary steps in constructing such model with a programming approach. A 'technical-only' quantitative model is rare today, and without much reference to follow, subjective and fundamental factors are usually included in constructing such portfolio. Therefore, the report has exhibited the assumptions, subjective decisions, and all influential elements for the designing and modeling processes in detail. 

Following the model flow chart, the sections below will illustrate the the `base model`, include computations, visualizations, analyses, simulations and etc.  

翻译 

*\textcolor{red}{Code Hidden 代码已隐藏}* 

```{r message=FALSE, warning=FALSE, include=FALSE}
# Data Intake
mega7data = read.csv("mega7tidy.csv")
mega7mcap = read.csv("mega7marketcap.csv")
```

```{r eval=FALSE, message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
# Full data part data intake for loop 

# Web-scrape SP500 stock list
sp_500_stock_list <- 
 read_html("https://en.wikipedia.org/wiki/List_of_S%26P_500_companies") %>%
  html_node("table.wikitable") %>%
  html_table() %>%
  select(`Ticker symbol`, Security, `GICS Sector`, `GICS Sub Industry`) %>%
  as_tibble()
# Format names
names(sp_500_stock_list) <- 
  sp_500_stock_list %>% 
  names() %>% 
  str_to_lower() %>% 
  make.names()
# Show results
sp_500_stock_list
```

```{r include=FALSE}
# Full data part data intake for loop 
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
# Data cleanup & add marketcap column to the main dataframe
mega7data_modified <- 
  mega7data %>%
  inner_join(mega7mcap, join_by(symbol == Stock)) %>%
  rename(market_cap = Marketcap) %>%
  select(!X.x) %>% 
  select(!X.y) 
```  

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.pos='H'}
kbl(tail(mega7data_modified,10), booktabs = T, linesep = "", 
    digits = 1, caption = "Cleaned Data Glance: NYSE and NASDAQ Stocks", 
    format.args = list(big.mark = ",", scientific = FALSE)) %>%
  kable_styling(latex_options = c("striped","scale_down",
                                  "HOLD_position"), 
                position = "center") %>%
  column_spec(c(3,8,9,10), bold = T) %>%
  footnote(general = "Output 2.1.a: Last 10 rows are shown.")
```

## Portfolio-specific Subjective Indicators 其他组合相关过滤指标

With over 6,000 stocks currently lists on the U.S. stock exchanges, the model will first eliminate the 'inappropriate' stocks, i.e. the stocks will not be considered as viable investment opportunities.

The following are the areas we take into considerations in eliminating the 'inappropriate' stocks:

* Investment needs/preset goals & risk preferences (specific to the managed portfolio)
* Management styles (avoid style drift or inconsistent investment styles)
* Liquidity requirements
* Client/Investor needs & risk tolerance
* Internal RM guidelines & compliance requirements

To reiterate, the eliminated stocks are dropped (from the potential investment list) due to the above subjective reasons; in no means these stocks will necessarily bring negative investment returns, some of them could bring substantial (positive) future returns. 

翻译

Thus, we set the following **subjective indicators** to meet the strategy needs (this list may be modified with the fast-changing market landscape): 

(1) $\text{Market Cap}> \$ 7 \text{ billion}$  
(2) $\text{Average Weekly Volume}> 1 \text{ million}$  
(3) $\text{Daily Return} \nless -15\%$  
(4) $\text{Annualized Volatility}\ngtr 100\%$.

翻译.  

### <span style="color:blue">Subjective Indicator No.1: Market Cap > \$ 7 billion</span>  

The program gathers the most up-to-date (value at close on the last trading day) *market cap* (`market_cap`) for each company, the stocks with a latest market cap smaller than 7 billion USD will be eliminated (from the stock selection list).  

A market cap less than $7 billion, indicates the stock is more growth in nature, and with less analyst coverage. 'Growth stocks' have the growth potential, however tend to be more volatile. To match the investment goals/portfolio needs, satisfy internal RM and compliance guidelines, and actively controlling the drawdown and down-side risks; the model therefore in advance, eliminates these stocks and label them as 'inviable' investment options.  

翻译  

*\textcolor{red}{Code Hidden 代码已隐藏}*  

```{r echo=FALSE, message=FALSE, warning=FALSE}
cap_remove_list_intermed <-
  mega7data_modified %>%
  filter(market_cap < 7e+9) 

cap_remove_list <- 
  pull(cap_remove_list_intermed, symbol)  %>%
  unique()
``` 

```{r echo=FALSE, message=FALSE, warning=FALSE}
mega7data_modified <- 
  mega7data_modified %>%
  filter(!symbol %in% cap_remove_list)

print(cap_remove_list)
```

Above output shows the `cap_remove_list`, i.e. the stocks removed from the `stockdata` dataset due to its *market cap* was smaller than 7 billion USD ($7\times 10^9$) some time during last year, to meet internal RM guidelines, and actively manage the potential downside risks and return fluctuation (drawdown) issues.  

翻译 

### <span style="color:blue">Subjective Indicator No.2: Average Weekly Volume > 1 million</span>  

The program first computes the average weekly (trading) `Volume`, the stock with an `average volume` **smaller than 1 million** some time during the last year, will be eliminated (from the stock list).  

A daily (average) trading volume of 1 million or less, indicates the stock was traded  inactively in relative terms. To satisfy internal RM and compliance guidelines, and avoid any liquidity risks; the model therefore in advance, eliminates these stocks and label them as 'inviable' investment options.  

翻译. 

*\textcolor{red}{Code Hidden 代码已隐藏}*  

```{r echo=FALSE, message=FALSE, warning=FALSE}
mega7data_modified <-
  mega7data %>% 
  mutate(week = strftime(date,format = "%V")) %>%
  mutate(year  = year(ymd(date)))
```

```{r echo=FALSE, message=FALSE, warning=FALSE,fig.pos='H'}
weekavg_volume <-
  mega7data_modified %>%
  group_by(year,week,symbol) %>%
  mutate(average.volume = mean(volume)) %>%
  ungroup() %>%
  select(year, week, date, symbol, average.volume) 
```

```{r eval=FALSE, fig.pos='H', message=FALSE, warning=FALSE, include=FALSE}
# pdf output
kbl(tail(weekavg_volume,10), booktabs = T, linesep = "",
    digits = 1, caption = "Average Weekly Trading Volume", 
    format.args = list(scientific = FALSE), longtable = T,
    col.names = c("Year","Week","Date","Symbol","Average Volume")) %>%
  kable_styling(latex_options = c("striped", "scale_down",
                                  "HOLD_position"), 
                position = "center") %>%
  column_spec(c(5), bold = T) %>%
  footnote(general = "Output 2.2.a: Last 10 rows are shown.")
```

```{r eval=FALSE, fig.pos='H', message=FALSE, warning=FALSE, include=FALSE}
# html Output


# Sample data (replace this with your actual data)
# Assume you have a data frame named all_stock_data containing data for all stocks
# The data frame should have columns: Date, Stock, Price, Volume, and any other relevant columns
# Each stock should be identified by a unique value in the Stock column
# The Date column should be in Date format
# Example: all_stock_data <- data.frame(Date = seq(as.Date("2019-01-01"), by = "day", length.out = 5*365),
#                                      Stock = rep(c("Stock1", "Stock2", "Stock3"), each = 5*365),
#                                      Price = rnorm(5*365*3, mean = 100, sd = 5),
#                                      Volume = rnorm(5*365*3, mean = 100000, sd = 20000))

# Define UI
ui222 <- fluidPage(
  titlePanel("Average Weekly Trading Volume"),
  sidebarLayout(
    sidebarPanel(
      selectInput("stock", "Select Stock:", choices = unique(weekavg_volume$symbol)),
      dateRangeInput("date_range", "Select Date Range:",
                     start = min(weekavg_volume$date),
                     end = max(all_stock_data$Date),
                     min = min(all_stock_data$Date),
                     max = max(all_stock_data$Date))
    ),
    mainPanel(
      DTOutput("data_table")
    )
  )
)

# Define server logic
server <- function(input, output) {
  
  # Filter data based on selected stock and date range
  filtered_data <- reactive({
    req(input$stock, input$date_range)
    subset(all_stock_data, Stock == input$stock & Date >= input$date_range[1] & Date <= input$date_range[2])
  })
  
  # Render interactive data table
  output$data_table <- renderDT({
    datatable(filtered_data(), options = list(pageLength = 10)) # Adjust page length as needed
  })
}

# Run the application
shinyApp(ui = ui, server = server)
```



```{r echo=FALSE, message=FALSE, warning=FALSE}
volume_remove_list_intermed <-
  weekavg_volume %>%
  filter(average.volume < 1e+6) 

volume_remove_list <- 
  pull(volume_remove_list_intermed, symbol)  %>%
  unique()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
mega7data_modified <- 
  mega7data_modified %>%
  filter(!symbol %in% volume_remove_list)

print(volume_remove_list)
```

Above output shows the `volume_remove_list`, i.e. the stocks removed from the `stockdata` dataset due to its `average volume` was smaller than 1 million ($1\times 10^6$) some time during last year, to avoid potential liquidity issues.  

翻译 

### <span style="color:blue">Subjective Indicator No.3: Daily Return $\nless -15\%$</span> 

The program first computes the *daily return* (`price_pctchange`), i.e. the *daily price* (`adjusted`) change in percentages for each stock. Any stock with a 'price drop' of more than 15\% in any trading day during the last year will be eliminated (from the stock selection list). FYI, the program utilizes the daily *adjusted close price* (`adjusted`) as the *daily price* for each stock inputs to the model, which they are adjusted for any dilutions to the shares, i.e. accounts for any dividend distributions and applicable share splits.    

A daily price change of -15\% indicates extreme short-term price down movement. To proactively manage (max) drawdown for our portfolio, the model therefore in advance, eliminates these stocks, which exhibited significant short-term downside risks during last year.  

翻译

*\textcolor{red}{Code Hidden 代码已隐藏}*  

```{r echo=FALSE, message=FALSE, warning=FALSE}
mega7data_modified <-
  mega7data_modified %>% 
  group_by(symbol) %>%
  mutate(price_pctchange = (adjusted/lag(adjusted)-1)*100)

pctchange_display <-
  mega7data_modified %>% 
  select(symbol,date,adjusted,price_pctchange) %>%
  tail(10)
```

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.pos='H'}
kbl(pctchange_display, booktabs = T, linesep = "",
    digits = 4, caption = "Price Percentage Change (1-day ROC)", 
    format.args = list(big.mark = ",", scientific = FALSE),
    col.names = c("Symbol","Date","Adj Close","Price Change %")) %>%
  kable_styling(latex_options = c("striped", "scale_down", 
                                  "HOLD_position"), 
                position = "center") %>%
  column_spec(c(3,4), bold = T) %>%
  footnote(general = "Output 2.2.b: Last 10 rows are shown.")
```

*\textcolor{red}{Code Hidden 代码已隐藏}*  

```{r echo=FALSE, message=FALSE, warning=FALSE}
prcpct_remove_list_intermed <-
  mega7data_modified %>%
  filter(price_pctchange < -15) 

prcpct_remove_list <- 
  pull(prcpct_remove_list_intermed, symbol)  %>%
  unique()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
mega7data_modified <- 
  mega7data_modified %>%
  filter(!symbol %in% prcpct_remove_list)

print(prcpct_remove_list)
```

Above output shows the `prcpct_remove_list`, i.e. the stocks removed from the `stockdata` dataset due to its *daily return* was smaller than $-15\%$, some time during last year, to manage short-term drawdown.  

翻译

### <span style="color:blue">Subjective Indicator No.4: Annualized volatility $\ngtr 100\%$</span>

The program first computes the (implied) *Annualized Volatility* from the *daily return*s  (`price_pctchange`) for each stock, using $\text{Annualized Volatility}=\Delta(\text{Daily Price})\cdot \sqrt{252}$, assuming 252 trading days every year. Any stock with an implied annual volatility of more than 100\% will be removed from the selection (process). 

Implied volatility (`annual_volatility`) greater than 100\% indicates extreme volatile price movements at some point during the last year. To actively manage potential short-term and long-term (portfolio) risks, and utilizing an equilibrium investment strategy; with the potential volatile stocks are exhibited, they will be eliminated in advance for that purpose.  

翻译

*\textcolor{red}{Code Hidden 代码已隐藏}*  

```{r echo=FALSE, message=FALSE, warning=FALSE}
mega7data_modified <-
  mega7data_modified %>%
  mutate(annual_volatility = price_pctchange * sqrt(252)) 

annual_volatility_display <-
  mega7data_modified %>%
  select(date, adjusted, symbol, annual_volatility) %>%
  na.omit() %>%
  tail(10)
``` 

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.pos='H'}
kbl(annual_volatility_display, booktabs = T, linesep = "",
    digits = 4, caption = "Implied Annualized Volatility", 
    format.args = list(big.mark = ",", scientific = FALSE),
    col.names = c("Date","Adj Close","Symbol","Annual Volatility %")) %>%
  kable_styling(latex_options = c("striped", "scale_down",
                                  "HOLD_position"), 
                position = "center") %>%
  column_spec(c(2,4), bold = T) %>%
  footnote(general = "Output 2.2.c: Last 10 rows are shown.")
```

*\textcolor{red}{Code Hidden 代码已隐藏}*  

```{r echo=FALSE, message=FALSE, warning=FALSE}
volat_remove_list_intermed <-
  mega7data_modified %>%
  filter(abs(annual_volatility) > 200) # change to 100

volat_remove_list <- 
  pull(volat_remove_list_intermed, symbol)  %>%
  unique()
```

```{r echo=FALSE, message=FALSE, warning=FALSE}
mega7data_modified <- 
  mega7data_modified %>%
  filter(!symbol %in% volat_remove_list)

print(volat_remove_list)
```

Above output shows the `volat_remove_list`, i.e. the stocks removed from the `stockdata` dataset due to its *annualized volatility* (`annual_volatility`) was greater than $100\%$, some time during last year, to actively control unusual return fluctuations and manage downside risks.  

翻译

*\textcolor{red}{Code Hidden 代码已隐藏}*  

```{r echo=FALSE, message=FALSE, warning=FALSE, fig.pos='H'}
# ADD STOCK REMOVED COMP NAME FULL, GICS SECTOR 
remove_stock_list <- 
  t(rbind(cap_remove_list,volume_remove_list,prcpct_remove_list,volat_remove_list)) 

colnames(remove_stock_list) <- "remove_stock_list"

kbl(tail(remove_stock_list,10), booktabs = T, linesep = "", 
    col.names = "Symbol" , 
    caption = "Stocks Removed by the Subjective Indicators") %>%
  kable_styling(latex_options = c("striped", "scale_down",
                                  "HOLD_position"), 
                position = "center", full_width = T) %>%
  column_spec(c(2), bold = T) %>%
  footnote(general = "Output 2.2.c: Last 10 rows are shown.",
           symbol = "In no means these removed stocks will bring negative investment returns, some of them may bring substantial (positive) future returns.")
```

In summary, above are the programming steps of the selection model, in eliminating the 'inappropriate' stocks; to suit specific investment needs/goals, portfolio risk preferences, and meet other internal RM guidelines and requirements. The 4 **subjective indicators** have removed a total **6** U.S. stocks (see the `remove_stock_list` output below) from the potential stock selection list for further modeling and analyzing (**constantly updating by model design, result as of 2024.03.09**).  

* To reemphasize, the stocks on the `remove_stock_list` were eliminated subject to the preset **subjective indicators** listed above. This particular list of indicators are dynamic, which may be adjusted (added/subtracted/modified) to fulfill investment needs based on the changing market landscape.   

* For practical portfolio constructions, more **subjective indicators** should be added, for example, stocks on the government's (so called) 'Entity List', should be eliminated to meet compliance (e.g. Lockheed Martin [LMT.NYSE], RTX Corporation [RTX.NYSE], etc).  

翻译. 






